Code for Graphs for ASN presentation

### 2020-12-07 ASNCode.Rmd
Changed some colors, added some graphs

emerged: #66CB5D
wander: #21908D
wowe: #3E4F8A
wowe mongo: #450F57

@@

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = fate), data = DCdata) +
  theme_bw() + 
  geom_point(alpha = 0.8) + 
  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450F57")) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)")
```

>>>>

emerged: #66CB5D
wander: #21908D
wowe: #3E4F8A
wowe mongo: #450D54

### Wasp fate

@@

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = fate), data = DCdata) +
  theme_bw() + 
  geom_point(alpha = 0.8) + 
  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
       color = "Developmental Outcome")
```

```{r}
dataPHS <- data[data$treatment == "P HS", ]

ggplot(aes(x = ttmax, y = mass.max, color = fate), data = dataPHS) +
  theme_bw() + 
  geom_point(alpha = 0.8) + 
  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
       color = "Developmental Outcome")
```

### Maximum mass compared to plant matter consumed

```{r}
ggplot(aes(x = area, y = mass.max), data = DCdata) + 
  theme_bw() + 
  geom_point(aes(color = fate)) + 
  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) +
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
       color = "Developmental Outcome")
```
```{r}
